% Declaration of Independence
% ---------------------------------------------------------------------------------------
\section*{Declaration of Independence}%
I hereby declare that I produced this thesis without prohibited external assistance and that none other than the listed references and tools have been used. I did not make use of any commercial consultant concerning graduation. A third party did not receive any nonmonetary perquisites neither directly nor indirectly for activities which are connected with the contents of the presented thesis.

All sources of information are clearly marked, including my own publications.

In particular I have not consciously:%
\begin{itemize}%
	\item Fabricated data or rejected undesired results,%
	\item misused statistical methods with the aim of drawing other conclusions than those warranted by the available data,%
	\item Plagiarized data or publications and%
	\item Presented the results of other researchers in a distorted way.%
\end{itemize}%
I do know that violations of copyright may lead to injunction and damage claims of the author and also to prosecution by the law enforcement authorities.

I hereby agree that the thesis may need to be reviewed with an electronic data processing for plagiarism.

This work has not yet been submitted as a doctoral thesis in the same or a similar form in Germany or in any other country. It has not ye been published as a whole
\vspace{1cm}%
\begin{flushleft}%
-----------------------------------------------\\%
Surname, Forename%%
\hfill%
Location, XX.XX.XXXX%
\end{flushleft}%
% ---------------------------------------------------------------------------------------
% End of File
